### 2020-08-25 2_task_bench.tex
Clarify that listing 1 is an excerpt.
Edit paragraph about MPI implementation.

Listing~\ref{lst:code-sample} shows an excerpt from the Task Bench
implementation in MPI. Methods of the \lstinline{Graph} object
\lstinline{g} are provided by Task Bench's core API and are shared
among all implementations. These methods are summarized in
Table~\ref{tab:api}. The MPI implementation follows the style of
communicating sequential processes, and simply executes a set of send
and receive calls (lines 24 and 16, respectively) followed by
executing the task body (line 32). For simplicity, the excerpt
assumes the number of MPI ranks is equal to the width of the graph;
the full implementation is more general and provides additional
optimizations. Despite its simplicity, this MPI implementation is
among our best performing, and shows that Task Bench can be mapped to
idiomatic code even in programming systems with no native concept of
task.

@@

In addition to specifying the shape of the task graph, the
core API also provides implementations of the kernels
executed by each task as well as other utility routines (to parse
inputs and display results). A sample of the core API compute kernel
is shown in Listing~\ref{lst:compute-kernel}. In addition to reducing
the effort required to implement Task Bench, providing central
implementations of these services ensures that all Task Bench
implementations can be scripted uniformly and eliminates a potential
source of performance disparity that can be a pitfall for other benchmarks.

>>>>

Listing~\ref{lst:code-sample} shows an excerpt from the Task Bench
implementation in MPI. Methods of the \lstinline{Graph} object
\lstinline{g} are provided by Task Bench's core API and are shared
among all implementations. These methods are summarized in
Table~\ref{tab:api}. The MPI implementation follows the style of
communicating sequential processes (CSP), and executes a set of send
and receive calls (lines 24 and 16, respectively) followed by
executing the task body (line 32). Despite MPI having no notion of
task, the execution of a task graph maps into the CSP style in a
straightforward way. The implementation is both simple and efficient,
but do to the choice of CSP makes no attempt to exploit task
parallelism, and leaves performance on the table when executing task
graphs with load imbalance or communication. Note the excerpt is
simplified for presentation and the full implementation is more
general and provides additional optimizations.

@@

In addition to specifying the shape of the task graph, the
core API also provides implementations of the kernels
executed by each task as well as other utility routines (to parse
inputs and display results). An excerpt from the core API compute kernel
is shown in Listing~\ref{lst:compute-kernel}. In addition to reducing
the effort required to implement Task Bench, providing central
implementations of these services ensures that all Task Bench
implementations can be scripted uniformly and eliminates a potential
source of performance disparity that can be a pitfall for other benchmarks.
